---
title: "AI in Education"
author: "Namig Abbasov"
format: html
editor: visual
---

## Libraries

```{r}
#install.packages("tidyverse")   
#install.packages("janitor")     # Clean messy Qualtrics column names
#install.packages("labelled")    # Manage Qualtrics labels
#install.packages("cregg")       # Conjoint analysis (AMCE, marginal means)
#install.packages("lme4")        # Mixed-effects regressions
#install.packages("broom")       # Tidy model summaries
#install.packages("sjPlot")      # Regression & AMCE visualization
#install.packages("performance") # Model diagnostics
#install.packages("ggthemes")    # Clean ggplot themes
#install.packages("scales")      # Better axis formatting for plots
#install.packages("patchwork")   # Combine multiple ggplots


library(tidyverse)
library(janitor)
library(labelled)
#library(cregg)
library(lme4)
library(broom)
library(sjPlot)
library(performance)
library(ggthemes)
library(scales)
library(patchwork)
library(emmeans)
library(ggplot2)
library(broom.mixed)
library(dplyr)
```

## Load Data

```{r}
raw <- read_csv("AI in Education_November 21, 2025_11.06.csv")

### Keep only completed responses
raw <- raw %>% filter(Progress == 100)

### Check how many respondents remain
n_distinct(raw$ResponseId)
```

## Reshape

```{r}
### Gather only conjoint columns (Q157–Q191)
conjoint_long <- raw %>%
  pivot_longer(
    cols = matches("^Q1(57|59|61|63|65|67|69|71|73|75|77|79|81|83|85|87|89|91)_\\d+$"),
    names_to = c("qid", "dv_num"),
    names_pattern = "(Q\\d+)_(\\d+)",
    values_to = "rating"
  ) %>%
  mutate(
    dv = case_when(
      dv_num == "1" ~ "usefulness",
      dv_num == "2" ~ "support_slider",
      dv_num == "3" ~ "autonomy"
    )
  )

### create lookup for profile attributes
profile_lookup <- tribble(
  ~qid, ~profile_id, ~materials, ~grading, ~support,
  "Q157", 1, "No AI", "Human only", "No chatbot",
  "Q159", 2, "No AI", "Human only", "Chatbot",
  "Q161", 3, "No AI", "AI reviewed", "No chatbot",
  "Q163", 4, "No AI", "AI reviewed", "Chatbot",
  "Q165", 5, "No AI", "AI unreviewed", "No chatbot",
  "Q167", 6, "No AI", "AI unreviewed", "Chatbot",
  "Q169", 7, "AI reviewed", "Human only", "No chatbot",
  "Q171", 8, "AI reviewed", "Human only", "Chatbot",
  "Q173", 9, "AI reviewed", "AI reviewed", "No chatbot",
  "Q175", 10, "AI reviewed", "AI reviewed", "Chatbot",
  "Q177", 11, "AI reviewed", "AI unreviewed", "No chatbot",
  "Q179", 12, "AI reviewed", "AI unreviewed", "Chatbot",
  "Q181", 13, "AI unreviewed", "Human only", "No chatbot",
  "Q183", 14, "AI unreviewed", "Human only", "Chatbot",
  "Q185", 15, "AI unreviewed", "AI reviewed", "No chatbot",
  "Q187", 16, "AI unreviewed", "AI reviewed", "Chatbot",
  "Q189", 17, "AI unreviewed", "AI unreviewed", "No chatbot",
  "Q191", 18, "AI unreviewed", "AI unreviewed", "Chatbot"
)

### Merge lookup and reshape so each profile is one row per participant
conjoint_clean <- conjoint_long %>%
  left_join(profile_lookup, by = "qid") %>%
  filter(!is.na(rating)) %>%   # keep only answered profiles
  pivot_wider(
    id_cols = c(ResponseId, profile_id, materials, grading, support),
    names_from = dv,
    values_from = rating
  )

### check results
glimpse(conjoint_clean)
nrow(conjoint_clean)            
n_distinct(conjoint_clean$ResponseId)
```

## Prepare IVs
```{r}
conjoint_clean <- conjoint_clean %>%
  mutate(
    materials = factor(materials,
                       levels = c("No AI", "AI reviewed", "AI unreviewed")),
    grading = factor(grading,
                     levels = c("Human only", "AI reviewed", "AI unreviewed")),
    support = factor(support,
                     levels = c("No chatbot", "Chatbot"))
  )
```


```{r}
### base
summary(conjoint_clean$usefulness)
summary(conjoint_clean$support_slider)
summary(conjoint_clean$autonomy)

### tidy overview
conjoint_clean %>%
  summarise(
    N = n(),
    respondents = n_distinct(ResponseId),
    mean_usefulness = mean(as.numeric(usefulness), na.rm=TRUE),
    sd_usefulness   = sd(as.numeric(usefulness), na.rm=TRUE),
    mean_support    = mean(as.numeric(support_slider), na.rm=TRUE),
    sd_support      = sd(as.numeric(support_slider), na.rm=TRUE),
    mean_autonomy   = mean(as.numeric(autonomy), na.rm=TRUE),
    sd_autonomy     = sd(as.numeric(autonomy), na.rm=TRUE)
  )
```

## EDA

```{r}
### Ensure numeric
conjoint_clean <- conjoint_clean %>%
  mutate(
    usefulness = as.numeric(usefulness),
    support_slider = as.numeric(support_slider),
    autonomy = as.numeric(autonomy)
  )

### Publication theme
pub_theme <- theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5),
    axis.title.x = element_text(margin = margin(t = 8)),
    axis.title.y = element_text(margin = margin(r = 8)),
    panel.grid.minor = element_blank()
  )

### Histogram function with optional y-axis label
plot_dist <- function(var, title, show_y = FALSE) {
  ggplot(conjoint_clean, aes(x = {{ var }})) +
    geom_histogram(
      bins = 20,
      boundary = 0,
      closed = "left",
      color = "white",
      linewidth = 0.3
    ) +
    geom_vline(xintercept = 50, linetype = "dashed", linewidth = 0.6) +
    scale_x_continuous(
      limits = c(0, 100),
      breaks = seq(0, 100, 20)
    ) +
    labs(
      title = title,
      x = "Rating (0–100)",
      y = if (show_y) "Number of Profiles" else NULL
    ) +
    pub_theme +
    theme(
      axis.title.y = if (show_y) element_text() else element_blank(),
      axis.text.y  = if (show_y) element_text() else element_blank(),
      axis.ticks.y = if (show_y) element_line() else element_blank()
    )
}

### Build plots
p_use <- plot_dist(usefulness, "Perceived Usefulness", show_y = TRUE)
p_sup <- plot_dist(support_slider, "Support for AI Policies")
p_aut <- plot_dist(autonomy, "Perceived Autonomy")

### Combine
(p_use | p_sup | p_aut) +
  plot_annotation(
    title = "",
    theme = theme(
      plot.title = element_text(face = "bold", size = 15, hjust = 0.5)
    )
  )

```

```{r}
### prepare long-format DV data (raw, observed)
dv_long <- conjoint_clean %>%
  select(usefulness, support_slider, autonomy,
         materials, grading, support) %>%
  pivot_longer(
    cols = c(usefulness, support_slider, autonomy),
    names_to = "dv",
    values_to = "value"
  ) %>%
  mutate(
    value = as.numeric(value),
    dv = recode(
      dv,
      "usefulness" = "Perceived Usefulness",
      "support_slider" = "Support for AI Policies",
      "autonomy" = "Perceived Autonomy"
    )
  )

### stack IVs and create facet-specific level codes
dv_iv_long <- dv_long %>%
  pivot_longer(
    cols = c(materials, grading, support),
    names_to = "attribute",
    values_to = "level"
  ) %>%
  mutate(
    attribute = recode(
      attribute,
      "grading"   = "Assessments & Grading",
      "materials" = "Instructional Materials",
      "support"   = "Personalized Support"
    ),
    plot_level = case_when(
      attribute == "Assessments & Grading"   ~ paste0("G_", level),
      attribute == "Instructional Materials" ~ paste0("M_", level),
      attribute == "Personalized Support"    ~ paste0("S_", level)
    )
  )

### enforce correct level order within each facet
dv_iv_long$plot_level <- factor(
  dv_iv_long$plot_level,
  levels = c(
    # Grading
    "G_Human only", "G_AI reviewed", "G_AI unreviewed",
    # Materials
    "M_No AI", "M_AI reviewed", "M_AI unreviewed",
    # Support
    "S_No chatbot", "S_Chatbot"
  )
)

dv_iv_long$attribute <- factor(
  dv_iv_long$attribute,
  levels = c(
    "Assessments & Grading",
    "Instructional Materials",
    "Personalized Support"
  )
)

### Colors (oversight-based)
level_colors <- c(
  "G_Human only"   = "#2B2B2B",
  "G_AI reviewed"  = "#1F78B4",
  "G_AI unreviewed"= "#D7301F",
  "M_No AI"        = "#636363",
  "M_AI reviewed"  = "#1F78B4",
  "M_AI unreviewed"= "#D7301F",
  "S_No chatbot"   = "#636363",
  "S_Chatbot"      = "#BDBDBD"
)

### Final plot
final_eda_plot <- ggplot(
  dv_iv_long,
  aes(x = plot_level, y = value, fill = plot_level)
) +
  geom_boxplot(width = 0.6, outlier.alpha = 1) +
  coord_cartesian(ylim = c(0, 100)) +
  facet_grid(
    dv ~ attribute,
    scales = "free_x",
    switch = "y"
  ) +
  scale_fill_manual(values = level_colors) +
  scale_x_discrete(labels = function(x) sub("^[A-Z]_", "", x)) +
  guides(fill = "none") +
  labs(
    x = NULL,
    y = "Rating (0–100)"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    strip.text.y.left = element_text(face = "bold"),
    strip.text.x = element_text(face = "bold"),
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(size = 11)
  )

print(final_eda_plot)
```

## Models

```{r}
model_usefulness <- lmer(as.numeric(usefulness) ~ materials + grading + support + (1 | ResponseId),
                         data = conjoint_clean)

model_support <- lmer(as.numeric(support_slider) ~ materials + grading + support + (1 | ResponseId),
                      data = conjoint_clean)

model_autonomy <- lmer(as.numeric(autonomy) ~ materials + grading + support + (1 | ResponseId),
                       data = conjoint_clean)
```

## Marginal Means
- Three graphs, one for each outcome variable. 
- Shows predicted outcome for a full profile, e.g. No AI + Human Only + No Chatbot
- Shouldn't go to paper as profiles are not what readers care for
- Conjoints are usually interpreted at the attribute level, not the profile level.
```{r}
emm_usefulness <- emmeans(model_usefulness, ~ materials + grading + support)
emm_support    <- emmeans(model_support,    ~ materials + grading + support)
emm_autonomy   <- emmeans(model_autonomy,   ~ materials + grading + support)


### Usefulness
plot(emm_usefulness, comparisons = TRUE) +
  labs(title = "Perceived Usefulness of AI Course Policies",
       y = "Predicted Rating (0–100)") +
  theme_minimal(base_size = 13)

### Support
plot(emm_support, comparisons = TRUE) +
  labs(title = "Support for AI Course Policies",
       y = "Predicted Rating (0–100)") +
  theme_minimal(base_size = 13)

### Autonomy
plot(emm_autonomy, comparisons = TRUE) +
  labs(title = "Perceived Autonomy under AI Course Policies",
       y = "Predicted Rating (0–100)") +
  theme_minimal(base_size = 13)
```

## Separate - 3 combined

```{r}
### Usefulness
emm_use_mat <- emmeans(model_usefulness, ~ materials)
emm_use_grad <- emmeans(model_usefulness, ~ grading)
emm_use_sup <- emmeans(model_usefulness, ~ support)

### Support
emm_sup_mat <- emmeans(model_support, ~ materials)
emm_sup_grad <- emmeans(model_support, ~ grading)
emm_sup_sup <- emmeans(model_support, ~ support)

### Autonomy
emm_aut_mat <- emmeans(model_autonomy, ~ materials)
emm_aut_grad <- emmeans(model_autonomy, ~ grading)
emm_aut_sup <- emmeans(model_autonomy, ~ support)

### function to make clean plots
plot_emm <- function(emm_obj, title, y_label) {
  plot(emm_obj, comparisons = FALSE) +
    labs(title = title,
         x = "Predicted Rating (0–100)",
         y = y_label) +
    theme_minimal(base_size = 13)
}

### usefulness plots
p_use_mat <- plot_emm(emm_use_mat, "Perceived Usefulness", "Materials")
p_use_grad <- plot_emm(emm_use_grad, "Perceived Usefulness", "Assessment & Grading")
p_use_sup <- plot_emm(emm_use_sup, "Perceived Usefulness", "Personalized Support")

### support plots
p_sup_mat <- plot_emm(emm_sup_mat, "Support for AI Policies", "Materials")
p_sup_grad <- plot_emm(emm_sup_grad, "Support for AI Policies", "Assessment & Grading")
p_sup_sup <- plot_emm(emm_sup_sup, "Support for AI Policies", "Personalized Support")

### autonomy plots
p_aut_mat <- plot_emm(emm_aut_mat, "Perceived Autonomy", "Materials")
p_aut_grad <- plot_emm(emm_aut_grad, "Perceived Autonomy", "Assessment & Grading")
p_aut_sup <- plot_emm(emm_aut_sup, "Perceived Autonomy", "Personalized Support")

### combine plots per DV
(p_use_mat | p_use_grad | p_use_sup) + plot_annotation(title = "Perceived Usefulness")
(p_sup_mat | p_sup_grad | p_sup_sup) + plot_annotation(title = "Support for AI Course Policies")
(p_aut_mat | p_aut_grad | p_aut_sup) + plot_annotation(title = "Perceived Autonomy")
```

## Separate - 9
```{r}
### helper plotting function
plot_emm <- function(model, variable, title, file_name) {
  emm <- emmeans(model, as.formula(paste0("~ ", variable)))
  p <- plot(emm, comparisons = FALSE) +
    labs(title = title,
         x = "Predicted Rating (0–100)",
         y = variable) +
    theme_minimal(base_size = 13)
  
  ggsave(filename = file_name, plot = p, width = 7, height = 5, dpi = 300)
  print(p)
}

### USEFULNESS
plot_emm(model_usefulness, "materials",
          "Perceived Usefulness by Course Materials",
          "usefulness_materials.png")

plot_emm(model_usefulness, "grading",
          "Perceived Usefulness by Grading Policy",
          "usefulness_grading.png")

plot_emm(model_usefulness, "support",
          "Perceived Usefulness by Chatbot Support",
          "usefulness_support.png")

### SUPPORT
plot_emm(model_support, "materials",
          "Support for AI Policies by Course Materials",
          "support_materials.png")

plot_emm(model_support, "grading",
          "Support for AI Policies by Grading Policy",
          "support_grading.png")

plot_emm(model_support, "support",
          "Support for AI Policies by Chatbot Support",
          "support_support.png")

### AUTONOMY
plot_emm(model_autonomy, "materials",
          "Perceived Autonomy by Course Materials",
          "autonomy_materials.png")

plot_emm(model_autonomy, "grading",
          "Perceived Autonomy by Grading Policy",
          "autonomy_grading.png")

plot_emm(model_autonomy, "support",
          "Perceived Autonomy by Chatbot Support",
          "autonomy_support.png")

```
## Coefficient plots
```{r}
### AMCE extraction
get_amce <- function(model, outcome_label) {
  tidy(model, effects = "fixed", conf.int = TRUE) %>%
    filter(term != "(Intercept)") %>%
    mutate(
      outcome = outcome_label,
      attribute = case_when(
        grepl("^materials", term) ~ "Instructional Materials",
        grepl("^grading", term) ~ "Assessments & Grading",
        grepl("^support", term) ~ "Personalized Support"
      ),
      level = case_when(
        term == "materialsAI reviewed" ~ "AI reviewed",
        term == "materialsAI unreviewed" ~ "AI unreviewed",
        term == "gradingAI reviewed" ~ "AI reviewed",
        term == "gradingAI unreviewed" ~ "AI unreviewed",
        term == "supportChatbot" ~ "Chatbot available",
        TRUE ~ term
      ),
      level = factor(
        level,
        levels = c(
          "AI unreviewed",
          "AI reviewed",
          "Chatbot available"
        )
      ),
      attribute = factor(
        attribute,
        levels = c(
          "Assessments & Grading",
          "Instructional Materials",
          "Personalized Support"
        )
      )
    )
}

amce_all <- bind_rows(
  get_amce(model_usefulness, "Perceived Usefulness"),
  get_amce(model_support, "Support for AI Course Policies"),
  get_amce(model_autonomy, "Perceived Autonomy")
)


### plot function 
plot_amce <- function(data, outcome_name) {
  ggplot(
    filter(data, outcome == outcome_name),
    aes(x = estimate, y = level)
  ) +
    geom_vline(
      xintercept = 0,
      linetype = "dashed",
      linewidth = 0.8,
      color = "gray35"
    ) +
    geom_errorbarh(
      aes(xmin = conf.low, xmax = conf.high),
      height = 0.18,
      linewidth = 0.8,
      color = "gray25"
    ) +
    geom_point(
      size = 3,
      color = "#008C7A"
    ) +
    facet_wrap(
      ~ attribute,
      scales = "free_y",
      nrow = 1
    ) +
    scale_x_continuous(
      limits = c(-25, 5),
      breaks = seq(-25, 5, 5)
    ) +
    labs(
      title = paste0("Effects of AI Policy Design on ", outcome_name),
      subtitle = "Reference categories: no AI materials, human grading, and no chatbot",
      x = "Average Marginal Component Effect (0–100 scale)",
      y = NULL
    ) +
    theme_minimal(base_size = 14) +
    theme(
      plot.title = element_text(face = "bold", hjust = 0.5, size = 18),
      plot.subtitle = element_text(hjust = 0.5, size = 14),
      strip.text = element_text(face = "bold", size = 13),
      panel.grid.minor = element_blank(),
      axis.text.y = element_text(size = 12),
      axis.text.x = element_text(size = 11),
      axis.title.x = element_text(size = 13, margin = margin(t = 8))
    )
}


### Generate plots

amce_usefulness_plot <- plot_amce(amce_all, "Perceived Usefulness")
amce_support_plot <- plot_amce(amce_all, "Support for AI Course Policies")
amce_autonomy_plot <- plot_amce(amce_all, "Perceived Autonomy")

amce_usefulness_plot
amce_support_plot
amce_autonomy_plot

### Save
ggsave(
  "figures/amce_usefulness.png",
  amce_usefulness_plot,
  width = 13,
  height = 5,
  dpi = 300,
  bg = "white"
)

ggsave(
  "figures/amce_support.png",
  amce_support_plot,
  width = 13,
  height = 5,
  dpi = 300,
  bg = "white"
)

ggsave(
  "figures/amce_autonomy.png",
  amce_autonomy_plot,
  width = 13,
  height = 5,
  dpi = 300,
  bg = "white"
)
```

### full first graph
```{r}
get_amce <- function(model, outcome_label) {
  tidy(model, effects = "fixed", conf.int = TRUE) %>%
    filter(term != "(Intercept)") %>%
    mutate(
      outcome = outcome_label,
      attribute = case_when(
        grepl("^materials", term) ~ "Instructional Materials",
        grepl("^grading", term) ~ "Assessments & Grading",
        grepl("^support", term) ~ "Personalized Support"
      ),
      level = case_when(
        term == "materialsAI reviewed" ~ "AI reviewed by instructor",
        term == "materialsAI unreviewed" ~ "AI without review",
        term == "gradingAI reviewed" ~ "AI reviewed by instructor",
        term == "gradingAI unreviewed" ~ "AI without review",
        term == "supportChatbot" ~ "Course chatbot",
        TRUE ~ term
      ),
      level = factor(
        level,
        levels = c(
          "AI reviewed by instructor",
          "AI without review",
          "Course chatbot"
        )
      ),
      attribute = factor(
        attribute,
        levels = c(
          "Assessments & Grading",
          "Instructional Materials",
          "Personalized Support"
        )
      )
    )
}

amce_all <- bind_rows(
  get_amce(model_usefulness, "Perceived Usefulness"),
  get_amce(model_support, "Support for AI Course Policies"),
  get_amce(model_autonomy, "Perceived Autonomy")
)



support_oversight_plot <- ggplot(
  filter(amce_all, outcome == "Support for AI Course Policies"),
  aes(x = estimate, y = level)
) +
  geom_vline(
    xintercept = 0,
    linetype = "dashed",
    linewidth = 0.8,
    color = "gray35"
  ) +
  geom_errorbarh(
    aes(xmin = conf.low, xmax = conf.high),
    height = 0.18,
    linewidth = 0.8,
    color = "gray25"
  ) +
  geom_point(
    size = 3,
    color = "#008C7A"
  ) +
  facet_wrap(
    ~ attribute,
    scales = "free_y",
    nrow = 1
  ) +
  scale_x_continuous(
    limits = c(-25, 5),
    breaks = seq(-25, 5, 5)
  ) +
  labs(
    title = "Student Support for AI Integration Depends on Human Oversight",
    subtitle = "Points indicate changes in support relative to fully human course policies",
    x = "Estimated Effect on Support (0–100 scale)",
    y = NULL,
    caption = "Negative values indicate lower support compared with fully human instructional materials, grading, and support."
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5, size = 18),
    plot.subtitle = element_text(hjust = 0.5, size = 13),
    plot.caption = element_text(hjust = 0.5, size = 10, color = "gray35"),
    strip.text = element_text(face = "bold", size = 13),
    panel.grid.minor = element_blank(),
    axis.text.y = element_text(size = 12),
    axis.text.x = element_text(size = 11),
    axis.title.x = element_text(size = 13, margin = margin(t = 8))
  )

support_oversight_plot

ggsave(
  "figures/support_oversight_plot.png",
  support_oversight_plot,
  width = 13,
  height = 5,
  dpi = 300,
  bg = "white"
)
```

### clean viz
```{r}
featured_data <- tibble(
  policy = c(
    "AI with\ninstructor review",
    "AI without\ninstructor review"
  ),
  effect = c(-5, -20)
)

featured_plot <- ggplot(
  featured_data,
  aes(
    x = effect,
    y = reorder(policy, effect),
    fill = policy
  )
) +
  geom_vline(
    xintercept = 0,
    linewidth = 1.3,
    color = "grey35"
  ) +
  geom_col(
    width = 0.55,
    show.legend = FALSE
  ) +
  geom_text(
    aes(
      label = sprintf("%.0f", effect),
      x = effect - 2.5
    ),
    size = 10,
    fontface = "bold"
  ) +
  scale_fill_manual(
    values = c(
      "AI with\ninstructor review" = "#B89B88",
      "AI without\ninstructor review" = "#D55E00"
    )
  ) +
  scale_x_continuous(
    limits = c(-25, 3),
    breaks = NULL
  ) +
  labs(
    title = "AI in Higher Education",
    subtitle = "Effects of instructor oversight on student support"
  ) +
  theme_void(base_size = 18) +
  theme(
    plot.title = element_text(
      size = 30,
      face = "bold",
      hjust = 0.5
    ),
    plot.subtitle = element_text(
      size = 16,
      hjust = 0.5,
      margin = margin(b = 25)
    ),
    axis.text.y = element_text(
      size = 18,
      face = "bold",
      color = "grey20",
      lineheight = 0.95
    ),
    plot.margin = margin(
      t = 30,
      r = 40,
      b = 30,
      l = 40
    )
  )

featured_plot

ggsave(
  "figures/featured_high_ed.png",
  featured_plot,
  width = 8,
  height = 5,
  dpi = 300,
  bg = "white"
)
```


## coefficient plots combined
```{r}
get_coefficients <- function(model, outcome_label) {
  tidy(model, effects = "fixed", conf.int = TRUE) %>%
    filter(term != "(Intercept)") %>%
    mutate(
      outcome = outcome_label,
      attribute = case_when(
        grepl("^materials", term) ~ "Instructional Materials",
        grepl("^grading", term) ~ "Assessments & Grading",
        grepl("^support", term) ~ "Personalized Support"
      ),
      level = case_when(
        term == "materialsAI reviewed" ~ "Materials: AI reviewed",
        term == "materialsAI unreviewed" ~ "Materials: AI unreviewed",
        term == "gradingAI reviewed" ~ "Grading: AI reviewed",
        term == "gradingAI unreviewed" ~ "Grading: AI unreviewed",
        term == "supportChatbot" ~ "Support: Chatbot available",
        TRUE ~ term
      ),
      level = factor(
        level,
        levels = c(
          "Support: Chatbot available",
          "Grading: AI reviewed",
          "Grading: AI unreviewed",
          "Materials: AI reviewed",
          "Materials: AI unreviewed"
        )
      ),
      outcome = factor(
        outcome,
        levels = c(
          "Perceived Usefulness",
          "Support for AI Course Policies",
          "Perceived Autonomy"
        )
      )
    )
}

coef_all <- bind_rows(
  get_coefficients(model_usefulness, "Perceived Usefulness"),
  get_coefficients(model_support, "Support for AI Course Policies"),
  get_coefficients(model_autonomy, "Perceived Autonomy")
)




coef_combined_plot <- ggplot(
  coef_all,
  aes(x = estimate, y = level, color = outcome)
) +
  geom_vline(
    xintercept = 0,
    linetype = "dashed",
    linewidth = 0.8,
    color = "gray35"
  ) +
  geom_errorbarh(
    aes(xmin = conf.low, xmax = conf.high),
    height = 0.18,
    linewidth = 0.8,
    position = position_dodge(width = 0.55)
  ) +
  geom_point(
    size = 2.8,
    position = position_dodge(width = 0.55)
  ) +
  scale_x_continuous(
    limits = c(-25, 5),
    breaks = seq(-25, 5, 5)
  ) +
  labs(
    title = "Effects of AI Policy Design on Student Evaluations",
    subtitle = "Reference categories: no AI materials, human grading, and no chatbot",
    x = "Estimated Effect on Rating (0–100 scale)",
    y = NULL,
    color = "Outcome"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5, size = 18),
    plot.subtitle = element_text(hjust = 0.5, size = 13),
    legend.position = "bottom",
    legend.title = element_text(face = "bold"),
    panel.grid.minor = element_blank(),
    axis.text.y = element_text(size = 12),
    axis.text.x = element_text(size = 11),
    axis.title.x = element_text(size = 13, margin = margin(t = 8))
  )

coef_combined_plot

ggsave(
  "figures/coefficient_plot_combined.png",
  coef_combined_plot,
  width = 11,
  height = 6,
  dpi = 300,
  bg = "white"
)
```

